---
title: "Inferring McDonalds's Geographic Strategy in the Brazilian Market"
output: html_notebook
---

This is an attempt to infer the strategy employed by McDonalds in determining the sites for its Brazilian locations. We begin by loading the data:

```{r}
library(tidyverse)

df = read.csv('data.csv', sep=';')
ref = read.csv('reference.csv', sep=';')
head(df)
```

```{r}
length(mac_pops) / length(pops)
```
We observe that $~3%$ of cities in Brazil have a McDonalds location. Hence, the naive inference is that McDonalds locations are randomly assigned according to a Bernoulli($p$) process where we estimate $$\hat{p}=0.0298$$

Turning to factors that may meaningfully influence the variable of interest, the most obvious choice is population (taken here as `IGBE_POP`). Unsurprisingly, the representatives of the subset of cities with McDonalds locations are larger than average: 
```{r}
mac_pops = df[!is.na(df$MAC),]$IBGE_POP
pops = df[!is.na(df$IBGE_POP),]$IBGE_POP
as.data.frame(cbind(
  stat = c('mean', 'median', 'min', 'max'),
  mac = c(mean(mac_pops), median(mac_pops), min(mac_pops), max(mac_pops)),
  nomac = c(mean(pops), median(pops), min(pops), max(pops))
))
```

However, we observe that population alone is not enough to infer the strategy:
```{r}
y = c()
z = c()
for (i in 1:length(mac_pops)) {
  y = c(y, length(df[df$IBGE_POP>=sort(mac_pops)[i],]$CITY))
  z = c(z, length(df[(df$IBGE_POP>=sort(mac_pops)[i] & !is.na(df$MAC)),]$CITY))
}

comp_df = as.data.frame(cbind(
  x=1:length(mac_pops),
  y=y,
  z=z
))

comp_df$p = comp_df$z / comp_df$y

ggplot(aes(x,1-p), data=comp_df) + geom_line(color='blue') + ggtitle('% of larger cities that do not have a mcdonalds')
```